### 2014-12-10 ms/ms.Rmd
Expanded description on search for data in ms Intro

We (D.S. Falster and R.A. Duursma, with the help of D.R. Barneche, R.G. FitzJohn and A. Vårhammar) set out to create such a resource, by asking authors directly whether they would be willing to make their raw data files freely available. The response was overwhelming: nearly everyone we contacted was interested to contribute their raw data. Moreover, we were invited to incorporate another compilation led by M.I. Ishihara and focusing on Japanese literature. As a result, we present BAAD: a Biomass And Allometry Database for woody plants, comprising data collected in `r length(unique(data$studyName))` different published and unpublished studies.

>>>>

We (D.S. Falster and R.A. Duursma, with the help of D.R. Barneche, R.G. FitzJohn and A. Vårhammar) set out to create such a resource. We identified data sources from existing collaborations as well as a wide-ranging literature search, focussed on woody plants in field as well as controlled conditions. We constrained the search by including only data where a wide range in plant sizes was measured, as well as a set of minimum variables (plant height and leaf mass or area), and an emphasis on field-grown plants (nearly all data from plants grown in controlled conditions arose from existing collaborations). We do not claim to have done an exhaustive search of the literature, due to the very large number of potential studies that could be included. In each case we asked authors directly whether they would be willing to make their raw data files freely available. The response was overwhelming: nearly everyone we contacted was interested to contribute their raw data. Moreover, we were invited to incorporate another compilation led by M.I. Ishihara and focusing on Japanese literature. As a result, we present BAAD: a Biomass And Allometry Database for woody plants, comprising data collected in `r length(unique(data$studyName))` different published and unpublished studies.
